---
title: "QC Report – CNVs Dataset"
output:
  pdf_document: default
  html_document: default
date: "Jacquemont Lab"
params:
  dataset_name: "dataset"
  path_dataset: "/lustre09/project/6008022/LAB_WORKSPACE/DATABASE/CNV/SPARK/Legacy_Array_GRCh38"
  path_CNVANNOTATION_repo: "/lustre09/project/6008022/LAB_WORKSPACE/SOFTWARE/Git_pipeline/CNV-Annotation/"
  path_CNVCALLER_repo: "/lustre09/project/6008022/LAB_WORKSPACE/SOFTWARE/Git_pipeline/CNV-Caller/"
---


<!-- 
Rscript -e 'rmarkdown::render("/lustre09/project/6008022/LAB_WORKSPACE/SOFTWARE/bioutils/bin/cnv_utils/cnv_dataset_report.Rmd", 
params=list(path_dataset="/lustre09/project/6008022/LAB_WORKSPACE/DATABASE/CNV/SPARK/SPARK_Array_GRCh37"), 
output_file="/home/flben/links/projects/rrg-jacquese/flben/report_qc_cnv_dataset/data/SPARK_Array_GRCh37.pdf")'
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(arrow)      # Parquet I/O
library(dplyr)      # Data manipulation
library(tidyr)      # Data reshaping
library(stringr)    # String utilities
library(ggplot2)    # Plotting
library(patchwork)  # Plot composition
library(viridis)    # Color palettes
library(scales)     # Axis formatting
library(rlang)
library(duckdb)
library(readxl)
library(ggh4x)
library(tidyverse)

## ===============================
## Paths and dataset metadata
## ===============================
path_dataset <- params$path_dataset
dataset_name <- basename(path_dataset)

if (params$dataset_name != "dataset"){
  dataset_name = params$dataset_name
}

path_CNVANNOTATION_repo <- params$path_CNVANNOTATION_repo
path_CNVCALLER_repo    <- params$path_CNVCALLER_repo


## ===============================
## Load CNV database
## ===============================
cnvDB <- read_parquet(paste(path_dataset,"/cnvDB.parquet",sep=""))

## Basic dataset statistics
sample_number <- n_distinct(cnvDB$SampleID)

```

# **Dataset:** `r str_replace_all(dataset_name,"_"," ")`  
### **Date:** `r format(Sys.Date(), "%d/%m/%Y")`
### **Number of samples carrying CNVs in the dataset:** `r scales::comma(sample_number)`

\vspace{0.5cm}

# 1- CNV length distribution

This section explores the **size distribution of CNVs** across the dataset, stratified by CNV type
(e.g. deletion, duplication).

Notes: We only study CNV with ProblematicRegions_Overlap < 0.5 to focus on high-confidence calls.

## A- Histogram of CNV lengths

\vspace{0.5cm}
```{r cnv-length-dist, echo=FALSE, warning=F, fig.width=6, fig.height=3}

## Remove ambiguous CNVs
cnvDB <- cnvDB %>%
  filter(Type == "DEL" | Type == "DUP") %>%
  filter(ProblematicRegions_Overlap < 0.5) %>%
  mutate(Length = End - Start + 1)

# Define the positions for annotations
annot_positions <- c(1e3, 1e4, 1e5, 1e6, 1e7, 1e8)  # bp

ggplot(cnvDB, aes(x = Length, fill = Type)) +   # map fill to Type
  geom_histogram(binwidth = 0.1, color = "white", position = "dodge") +  # stacked bars by default
  labs(x = "CNV Length (bp)", y = "Number of CNVs") +
  theme_bw() +
  theme(
    text =  element_text(size = 14),
    axis.title = element_text(size = 12),
    plot.title = element_text(size = 11),
    strip.text = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 11) 
  ) +
  annotation_logticks(sides = "bp") +
  scale_x_log10(labels = label_number(scale_cut = cut_si("bp")),
                lim = c(500, 1e7),
                breaks = annot_positions) +
  scale_fill_manual(values = c("DUP" = "steelblue", "DEL" = "tomato"))  # manually set two colors

```

\vspace{1cm}

## B- Counts per CNV type and size bin

\vspace{0.5cm}

```{r cnv-length-pie, echo=FALSE, warning=F, fig.width=7, fig.height=2}

# Bin CNV lengths
cnvDB <- cnvDB %>%
  mutate(
    LengthBin = cut(
      Length, 
      breaks = c(0, 1e4, 5e4, 1e5, 1e6, Inf),
      labels = c("1-10kb", "10-50kb", "50-100kb", "100kb-1Mb", ">1Mb"),
      include.lowest = TRUE
    )
  )

# Compute total per Type
total_counts <- cnvDB %>%
  group_by(Type) %>%
  summarise(TotalCount = scales::comma(n()), .groups = "drop")

# Join total count back to the CNV table
cnvDB <- cnvDB %>%
  left_join(total_counts, by = "Type") %>%
  mutate(FacetLabel = paste0(Type, " (N= ", TotalCount, ")"))

bin_counts <- cnvDB %>%
  group_by(LengthBin, FacetLabel) %>%
  summarise(Count = n(), .groups = "drop")

# Fix colors using viridis
length_bin_levels <- levels(factor(c("1-10kb", "10-50kb", "50-100kb", "100kb-1Mb", ">1Mb"),levels=c("1-10kb", "10-50kb", "50-100kb", "100kb-1Mb", ">1Mb")))
fixed_colors <- viridis::viridis(length(length_bin_levels), option = "D")
names(fixed_colors) <- length_bin_levels


ggplot(bin_counts, aes(x = "", y = Count, fill = LengthBin)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() +
  labs(
    fill = "CNV length category"
  ) +
  geom_text(data=bin_counts[bin_counts$Count > 10^(max(log10(bin_counts$Count))-2),],aes(label = Count), position = position_stack(vjust = 0.5), size = 4,color="white") +
  scale_fill_manual(values = fixed_colors) +
  facet_wrap(~FacetLabel, scales = "free",ncol=3)+
  theme(
    axis.title = element_text(size = 12),
    plot.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14) 
  )
```

\vspace{1cm}

## C- Counts per SampleID and CNV type

\vspace{0.5cm}
```{r cnv-per-sample, echo=FALSE, warning=F, fig.width=4, fig.height=5}

# 1. Compute CNV counts per sample, type, and size category (single pass)
boxplot_data <- cnvDB %>%
  mutate(
    Category = factor(
      if_else(Length < 50000, "Small (< 50kb)", "Large (>= 50kb)"),
      levels = c("Small (< 50kb)", "Large (>= 50kb)")
    )
  ) %>%
  group_by(SampleID, Type, Category) %>%
  summarise(count = n(), .groups = "drop") %>%
  complete(SampleID, Type, Category, fill = list(count = 0))

# 2. Compute automatic y-axis limits per facet (99th percentile cap)
auto_limits <- boxplot_data %>%
  group_by(Category, .drop = FALSE) %>%          # keep empty factor levels
  summarise(
    ymax = ceiling(quantile(count, 0.95) * 1.15),
    .groups = "drop"
  ) %>%
  mutate(ymax = ifelse(is.na(ymax) | ymax == 0, 1, ymax)) %>%  # avoid NA/0 limits
  deframe()

# 3. Build named scale list for facetted_pos_scales
y_scales <- setNames(
  lapply(names(auto_limits), function(cat) {
    scale_y_continuous(limits = c(0, auto_limits[[cat]]), oob = scales::squish)
  }),
  names(auto_limits)
)

# 2. Plot
ggplot(boxplot_data, aes(x = Type, y = count, fill = Type)) +
  
  geom_boxplot(outlier.size = 0.5, outlier.alpha = 0.2) +
  
  # Facet by CNV size
  facet_wrap(~Category, scales = "free_y", ncol = 1) +
  
  # Different y-axis limits per facet
  facetted_pos_scales(y = y_scales) +
  
  # Colors
  scale_fill_manual(values = c("DUP" = "steelblue", "DEL" = "tomato")) +
  
  # Labels
  labs(
  subtitle = paste0(
      "Zoom : ",
      "Small CNVs 0-", auto_limits[["Small (< 50kb)"]],
      ", Large CNVs 0-", auto_limits[["Large (>= 50kb)"]]
    ),
    x = "Variant Type",
    y = "Number of CNVs per sample"
  ) +
  
  # Theme
  theme_bw() +
  theme(
    axis.title = element_text(size = 12),
    text = element_text(size = 14),
    plot.subtitle = element_text(size = 10),
    strip.text = element_text(face = "bold", size = 12),
    strip.background = element_rect(fill = "grey95"),
    legend.position = "none",
    
    # Optional spacing between facets
    panel.spacing.y = unit(1, "cm")
  )
```

\newpage

# 2- Mendelian precision analysis

This analysis evaluates the **Mendelian precision** of CNV calls using parent–child trios.
For each CNV detected in the child, we assess whether a corresponding event is observed in at least one parent, given an overlap threshold of **25% reciprocal overlap**.

Mendelian precision is defined as the **fraction of child CNVs also observed in a parent**, and is reported as a function of **CNV length** and **CNV type**.
This metric provides a proxy for **call reliability**, with higher precision expected for larger CNVs.

The analysis is performed only if a valid `sampleDB.tsv` file containing trio information
(`SampleID`, `FatherID`, `MotherID`) is available.

```{r mendelian-possibility, echo=FALSE, warning=F, fig.width=5.5, fig.height=4}

mendelian_precision <- FALSE
number_trio = 0

sampleDB_path <- file.path(path_dataset, "sampleDB.tsv")

if (!file.exists(sampleDB_path)) {
  message("Mendelian precision analysis skipped: 'sampleDB.tsv' not found.")
} else {
  
  sampleDB <- read.delim(sampleDB_path)
  
  required_cols <- c("SampleID", "FatherID", "MotherID")
  missing_cols <- setdiff(required_cols, colnames(sampleDB))
  
  if (length(missing_cols) > 0) {
    message(
      "Mendelian precision analysis skipped: sampleDB.tsv is missing required columns: "
    )
    message(
      paste(missing_cols, collapse = ", ")
    )
  } else {
        # A 'trio' exists if a sample has both a Father and a Mother listed
        # We check that the IDs are not NA, not empty, and not "0"
        trios <- sampleDB[
          !is.na(sampleDB$FatherID) & sampleDB$FatherID != "" & sampleDB$FatherID != "0" &
          !is.na(sampleDB$MotherID) & sampleDB$MotherID != "" & sampleDB$MotherID != "0", 
        ]
    
        at_least_one_trio <- nrow(trios) > 0
    
        if (!at_least_one_trio) {
          message("Mendelian precision analysis skipped: No complete trios found in sampleDB.")
        } else {
              ## -------------------------------
              ## Run trio inheritance annotation
              ## -------------------------------
              cmd <- paste(path_CNVCALLER_repo,"/bin/make_report/cnv_trio_inheritance.py",sep="")
              
              dataset_name_file = str_split_1(path_dataset,"/")[length(str_split_1(path_dataset,"/"))]
              
              # Connect to an in-memory DuckDB database
              con <- dbConnect(duckdb::duckdb(), dbdir = ":memory:")
                
              # Filter CNVs to include only shared samples
              dbExecute(con, sprintf("
                CREATE TEMP TABLE cnv_gene_DB AS
                SELECT c.*
                FROM read_parquet('%s/cnvDB.parquet') c
                WHERE ProblematicRegions_Overlap < 0.5
              ", path_dataset))
              
              # Save CNV-gene table for this dataset
              dbExecute(con, sprintf("
                COPY cnv_gene_DB
                TO 'cnv_gene_DB_%s.parquet'
                (FORMAT PARQUET)
              ", dataset_name_file))
              
              # Disconnect from DuckDB
              dbDisconnect(con, shutdown = TRUE)

              system2(
                "python3",
                args = c(
                  cmd,
                  "-c", paste("cnv_gene_DB_", dataset_name_file,".parquet",sep=""),
                  "-p", paste(path_dataset,"/sampleDB.tsv",sep=""),
                  "-t", "Type",
                  "-f", "0.25"
                )
              )
              
              unlink(paste("cnv_gene_DB_", dataset_name_file,".parquet",sep=""), force = TRUE)

              ## -------------------------------
              ## Load annotated CNVs
              ## -------------------------------
              cnvDB_trio <- read.delim("annotated_child_cnv.tsv") %>%
                filter(Type == "DEL" | Type == "DUP")
              
              number_trio <- n_distinct(cnvDB_trio$SampleID) 

              if (number_trio == 0) {
                message("Mendelian precision analysis skipped: no child CNVs with trio information found.")
              } else {
              mendelian_precision <- TRUE
      }
    }
  }
}
```

## **Number of trios in the dataset:** `r scales::comma(number_trio)`

\vspace{0.5cm}

## A- Overall Mendelian precision

\vspace{0.5cm}
```{r mendelian-precision, echo=FALSE, warning=F, fig.width=5.5, fig.height=4}

if (!mendelian_precision) {
  message("Mendelian precision not possible: missing or incomplete sampleDB.tsv.")
} else {
    ## -------------------------------
    ## Bin CNV lengths
    ## -------------------------------
    cnvDB_trio <- cnvDB_trio %>%
      mutate(
        LengthBin = cut(
          Length, 
          breaks = c(0, 1e4, 5e4, 1e5, 1e6, Inf),  # in bp
          labels = c("1-10kb", "10-50kb", "50-100kb", "100kb-1Mb", ">1Mb"),
          include.lowest = TRUE
        )
      )
    
    
    ## -------------------------------
    ## Mendelian precision per bin
    ## -------------------------------
    mendelian_precision_df <- cnvDB_trio %>%
      group_by(LengthBin, Type) %>%
      summarise(
        Total_CNVs = n(),
        Avg_Length = mean(Length),
        Observed_in_Parent = sum(Observed_in_Parent_0.25 == "true", na.rm = TRUE),
        Mendelian_Precision = Observed_in_Parent / Total_CNVs,
        SE = sqrt(Mendelian_Precision * (1 - Mendelian_Precision) / Total_CNVs),
        .groups = "drop"
      )
    
    ## -------------------------------
    ## Plot
    ## -------------------------------
    ggplot(mendelian_precision_df, aes(x = LengthBin,y = Mendelian_Precision, color = Type)) +   # map fill to Type
      theme_bw() + geom_errorbar(aes(ymin = Mendelian_Precision - SE, ymax = Mendelian_Precision + SE), width = 0.1) +
      geom_point(size=2) +
      labs(
        x = "CNV length category",
        y = "Mendelian precision"
      ) + geom_text(aes(label=round(Mendelian_Precision,2)) ,hjust=-0.3) +
      scale_color_manual(values = c("DUP" = "steelblue", "DEL" = "tomato"))  + ylim(0,1)+
      theme(
        axis.title = element_text(size = 12),
        text =  element_text(size = 14),
        plot.title = element_text(size = 14),
        axis.text.x = element_text(size = 12, angle=30, vjust=0.5),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14) 
      )
    
}
```

\newpage

## B- Visual Guide for QC Threshold Selection


This section provides graphics that help to set manual filtering thresholds.

By observing the relationship between numeric metrics and Mendelian precision, you can visually determine at which score a metric becomes a reliable predictor of a "true" CNV.

\vspace{0.5cm}

```{r mendelian-message, echo=FALSE, warning=F, fig.width=5.5, fig.height=4}

if (!mendelian_precision) {
  message("Mendelian precision not possible: missing or incomplete sampleDB.tsv.")
}
```


```{r mendelian-precision-qc, echo=FALSE, warning=F, message=F, fig.width=11, fig.height=9}

if (mendelian_precision) {
  
    # 1. Global Data Preparation
    df_long <- cnvDB_trio %>%
      # Explicitly exclude position columns, IDs, and specific metrics not needed for study
      select(-matches("Start|End|Chr|SampleID|CNV_ID|rCNV_ID|sum_inv_LOEUF|Gnomad_Max_AF")) %>%
      # Create size groups and binary target
      mutate(
        target = as.numeric(as.logical(Observed_in_Parent_0.25)),
        group = if_else(Length >= 50000, "Large (>= 50kb)", "Small (< 50kb)")
      ) %>%
      # Pivot to long format for faceting (excluding metadata and grouping columns)
      pivot_longer(
        cols = where(is.numeric) & !c(target, Length), 
        names_to = "metric_name", 
        values_to = "metric_value"
      ) %>%
      drop_na(metric_value, target)

    # 2. Calculate Binned Statistics per Metric
    n_bins <- 20
    binned_all <- df_long %>%
      group_by(metric_name, group) %>%
      # Create metric-specific bins
      mutate(bin = cut(metric_value, breaks = n_bins)) %>%
      group_by(metric_name, group, bin) %>%
      summarise(
        mean_score = mean(metric_value, na.rm = TRUE),
        precision = mean(target, na.rm = TRUE),
        n = n(),
        .groups = 'drop'
      ) %>%
      filter(n > 10) %>%
      mutate(
        # Standard Error of the proportion
        se = sqrt((precision * (1 - precision)) / n),
        # 95% Confidence Interval
        lower = pmax(0, precision - 1.96 * se),
        upper = pmin(1, precision + 1.96 * se)
      )

    file.remove("annotated_child_cnv.tsv")

    # 3. Generate Panel (Facet Wrap)
    ggplot(binned_all, aes(x = mean_score, y = precision, color = group, fill = group)) +
      # Confidence intervals
      geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.15, color = NA) +
      # Trend lines
      geom_line(size = 1) +
      # Points sized by volume of data
      geom_point(aes(size = n), alpha = 0.6) +
      # Create one panel per QC metric with independent X axes
      facet_wrap(~ metric_name, scales = "free_x") + 
      scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
      scale_color_manual(values = c("Small (< 50kb)" = "#88CCEE", "Large (>= 50kb)" = "#117733")) +
      scale_fill_manual(values = c("Small (< 50kb)" = "#88CCEE", "Large (>= 50kb)" = "#117733")) +
      labs(
        title = "Systematic comparison of metrics (CNVs stratified by < 50kb vs >= 50kb)",
        x = "Metric Value",
        y = "Mendelian Precision (% Inherited)",
        size = "Number of CNVs",
        color = "Size Category", 
        fill = "Size Category"
      ) +
      theme_bw() +
      theme(
        legend.position = "bottom",
        strip.background = element_rect(fill = "grey90"),
        strip.text = element_text(face = "bold",size = 12)
      ) +
      theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.direction = "horizontal",
        text =  element_text(size = 17),
        plot.title = element_text(size = 17),
        axis.text.x = element_text(size = 12, angle=30, vjust=0.7),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 17) 
      ) + theme(
  panel.spacing.x = unit(0.5, "cm")  # increase horizontal space
)
  
}
```

\newpage

# 3- rCNV frequency comparison with UK Biobank–based studies

This analysis compares **recurrent CNV (rCNV) frequencies** observed in the current dataset
to frequencies reported in large external cohorts, primarily **UK Biobank–based studies**.

For each rCNV:

* Frequency is defined as the **percentage of samples carrying at least one event**
* Comparisons are performed **pairwise** between this dataset and published references
* Analyses are stratified by **rare (< 0.06%)** and **more frequent (> 0.06%)** rCNVs

\vspace{0.5cm}

```{r rcnv-frequency-comparison, echo=FALSE, warning=F, fig.width=10, fig.height=8}

## -------------------------------
## Load external rCNV frequencies
## -------------------------------
freq_rCNV <- read_excel(paste(path_CNVANNOTATION_repo,"/resources/rCNV/docs/frequency_comparison.xlsx",sep=""))

group_rCNV <- read.delim(paste(path_CNVANNOTATION_repo,"/resources/rCNV/geneset_per_rCNV.tsv",sep=""))
rownames(group_rCNV) = group_rCNV$rCNV_ID

freq_rCNV = freq_rCNV[,c("Reference","Group_ID","Frequency")]

freq_rCNV = freq_rCNV[freq_rCNV$Reference %in% c("Kendall et al, 2019","Crawford et al, 2019","supp_cecile_2025"),]
freq_rCNV$Reference <- str_replace_all(freq_rCNV$Reference, ",", "")



## -------------------------------
## Compute rCNV frequencies
## -------------------------------
number_samples <- n_distinct(cnvDB$SampleID)

base_id <- str_replace_all(cnvDB$rCNV_ID, "_del|_dup", "")
suffix  <- str_extract(cnvDB$rCNV_ID, "_del|_dup")

cnvDB$Group_ID <- paste0(
  group_rCNV[base_id, "Group_ID"],
  suffix
)


rCNV_stats <- cnvDB %>%
  group_by(Group_ID) %>%
  summarise(
    Reference = dataset_name,
    Count = n(),                     # how many times this rCNV appears
    Frequency = n_distinct(SampleID) / number_samples*100,  # fraction of samples carrying it
    .groups = "drop"
  )

rCNV_stats = rCNV_stats[,c("Reference","Group_ID","Frequency")]

merged_bins = rbind(rCNV_stats,freq_rCNV)


## -------------------------------
## Merge internal and external data
## -------------------------------
merged_bins <- merged_bins %>%
  filter(Frequency != "-" & !is.na(Frequency)) %>%
  mutate(Frequency = as.numeric(Frequency))

merged_bins <- merged_bins %>%
  mutate(
    Reference = gsub("[ ,]", "_", Reference)
  )

freq_wide <- merged_bins %>%
  pivot_wider(names_from = Reference, values_from = Frequency)


## -------------------------------
## Pairwise regression plots
## -------------------------------
plot_list <- list()
x_col = dataset_name
freq_threshold <- 0.06

for (label in c("Rare", "Common")) {
  for(y_col in colnames(freq_wide)[c(-1,-2)]) {
  
    plot_data <- freq_wide %>%
      filter(!is.na(.data[[x_col]]) & !is.na(.data[[y_col]])) %>%
      filter(
        if (label == "Rare") .data[[x_col]] <= freq_threshold
        else .data[[x_col]] > freq_threshold
      )
      
    # Check if we actually have data points to plot
    if (nrow(plot_data) > 1) {
      lm_fit <- lm(plot_data[[y_col]] ~ plot_data[[x_col]])
      r2 <- summary(lm_fit)$r.squared
      r2_label <- round(r2, 3)
    } else {
      # If no data, we set R2 to NA or 0 to avoid crashing
      r2_label <- "N/A"
    }
    p <- ggplot(plot_data, aes(x = .data[[x_col]], y = .data[[y_col]])) +
      geom_abline() +
      geom_point(pch = 21, size = 3, fill = "darkgrey", alpha = 0.8) +
      labs(
        x = paste0(str_replace_all(x_col,"_"," "), " frequency (%)"),
        y = paste0(str_replace_all(y_col,"_"," "), " frequency (%)"),
        title = paste0(
          label, " rCNVs (", 
          ifelse(label == "Rare", "<=", ">"),
          " 0.06%)\nR² = ", r2_label
        )
      ) +
      theme_bw() +
      theme(
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 14)
      )
    
    plot_list[[paste(y_col, label)]] <- p
  }
}

wrap_plots(plot_list, ncol = 3) & 
  theme(plot.margin = margin(t = 20, r = 5, b = 20, l = 5))

```


\newpage
# 4- Analysis of CNV gene constraint burden as a function of cumulative 1/LOEUF

This section describes the distribution of CNVs according to their **gene constraint burden**, measured as the cumulative 1/LOEUF of genes overlapped by each CNV.

For each CNV, `sum_inv_LOEUF` is defined as the sum of 1/LOEUF values for all canonical transcripts overlapping the CNV. Higher values indicate overlap with more constraint-intolerant genes.

CNVs affecting highly constrained genes are expected to be depleted compared to less constrained regions.

\vspace{0.5cm}


```{r cnv-loeuf-frequency, echo=FALSE, warning=F, fig.width=5.5, fig.height=3}

ggplot(cnvDB %>% filter(sum_inv_LOEUF > 0),
       aes(x = sum_inv_LOEUF, fill = Type)) +
  geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
  scale_x_log10() +
  theme_bw() +
  labs(
    x = "Cumulative 1/LOEUF per CNV",
    y = "Number of CNVs"
  ) +
  scale_fill_manual(values = c("DUP" = "steelblue", "DEL" = "tomato")) +
  annotation_logticks(sides = "bp")  +
  annotate(
    "text",
    x = Inf, y = Inf,
    label = sprintf(
      "Mean: %.2f\nMedian: %.2f",
      mean(cnvDB$sum_inv_LOEUF[cnvDB$sum_inv_LOEUF > 0], na.rm = TRUE),
      median(cnvDB$sum_inv_LOEUF[cnvDB$sum_inv_LOEUF > 0], na.rm = TRUE)
    ),
    size = 3,
    color = "black",
    hjust = 2,
    vjust = 1.3
  )+
  theme(
    text =  element_text(size = 14),
    axis.title = element_text(size = 12),
    plot.title = element_text(size = 11),
    strip.text = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 11) 
  ) 

```
